Calculating life expectancy and exploring missingness

### 2016-11-04 Code/1_Explore_Data_v2.Rmd
more changes

```{r fill_in_missing_counts}
dat.clean <- dat.clean %>% mutate(Count_md1 = ifelse(is.na(Count)==T, 1, Count),
                                  Count_md5 = ifelse(is.na(Count)==T, 5, Count),
                                  Count_md9 = ifelse(is.na(Count)==T, 9, Count)
                                  )

@@

dat2 <- merge(dat2, dat3, by = "StateYearRaceSex")
```

@@

BlackWhite <- BlackWhite %>% mutate(WBgap = le.birth.white - le.birth.black)

>>>>

```{r fill_in_missing_counts}
##NEED TO UPDATE THIS SO THAT CAN'T IMPUTAT COUNT > POP SIZE.
##FOLLOW UPDATE WITH RE-RUNNING THE MODELS.
dat.clean <- dat.clean %>% mutate(Count_md1 = ifelse(is.na(Count)==T, 1, Count),
                                  Count_md5 = ifelse(is.na(Count)==T, 5, Count),
                                  Count_md9 = ifelse(is.na(Count)==T, 9, Count)
                                  )

@@

dat2 <- merge(dat2, dat3, by = "StateYearRaceSex")

dat2 <- dat2 %>% arrange(State2, Year3, Race2, Sex2, Age3)
```

@@

BlackWhite <- BlackWhite %>% mutate(WBgap = le.birth.white - le.birth.black)
```
